---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lgrExtra

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) 
[![CRAN status](https://www.r-pkg.org/badges/version/lgrExtra)](https://CRAN.R-project.org/package=lgrExtra)
<!-- badges: end -->

Extra appenders for logging to push notifications, email, databases, and
other destinations for [lgr](https://github.com/s-fleck/lgr). Please
refer to the [function reference](https://s-fleck.github.io/lgrExtra/reference/index.html) 
for details and examples


# Development status

The appenders provided by lgrExtra are of varying stability. Elasticsearch
and Dynatrace are ready for production use (i use them in production), but 
Database-based appenders are still considered experimental and more of a 
prove-of-concept. 

| Appender                 | Description                                  | Backend                                                               | Status                                                                                                                                                       |
|--------------------------|----------------------------------------------|-----------------------------------------------------------------------|--------------------------------------------------------------------------------------------------------------------------------------------------------------|
| AppenderAWSCloudWatchLog | Amazon AWS CloudWatch Log                    | [paws.management](https://cran.r-project.org/package=paws.management) | [![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)  |
| AppenderElasticSearch    | ElasticSearch                                | [elastic](https://cran.r-project.org/package=elastic)                 | [![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)               |
| AppenderDbi              | Databases                                    | [DBI](https://cran.r-project.org/package=DBI)                         | [![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)  |
| AppenderDt               | In-memory data.table                         | [data.table](https://github.com/Rdatatable/data.table)                | [![Lifecycle: superseded](https://img.shields.io/badge/lifecycle-superseded-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html#superseded)          |
| AppenderGmail            | E-mail via Gmail REST API                    | [gmailr](https://cran.r-project.org/package=gmailr)                   | [![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)  |
| AppenderPool             | Databases (via connection pool)              | [pool](https://cran.r-project.org/package=pool)                       | [![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)  |
| AppenderPushbullet       | Pushbullet (mobile phone push notifications) | [RPushbullet](https://cran.r-project.org/package=RPushbullet)         | [![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)               |
| AppenderSendmail         | E-mail via SMTP                              | [sendmailR](https://cran.r-project.org/package=sendmailR)             | [![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)               |
| AppenderSyslog           | Linux Syslog                                 | [rsyslog](https://cran.r-project.org/package=rsyslog)                 | [![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)               |
| AppenderDynatrace        | Dynatrace                                    | [httr2](https://cran.r-project.org/package=httr2)                     | [![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)  |


## Installation

You can install the stable version from CRAN

```{r eval = FALSE}
install.packages("lgrExtra")
```

or the current development version directly from github

```{r eval = FALSE}
#install.packages("remotes")
remotes::install_github("s-fleck/lgrExtra")
```
